Assignment 2

### 2019-06-29 ex2/report/report.tex

As a downside of this approach, it is unclear whether a machine learning model learn to classify based on characteristics that are inherent to the attacks which should be detected, or rather learns to classify based on patterns that were unintentionally created during dataset generation.

>>>>

As a downside of this approach, it is unclear whether a machine learning model learns to classify based on characteristics that are inherent to the attacks which should be detected, or rather learns to classify based on patterns that were unintentionally created during dataset generation.
